Effort and Delay Discounting in a Foraging Environment

### 2019-04-25 Cost2/Cost2_prereg_remake.Rmd
overhaul of cost 2 prereg RMD, plus data cleaning/update

---
title: "Effort and Delay Discounting in a Foraging Environment"
author: "Claudio Toro Serey & Joseph T. McGuire"
output:
  pdf_document: default
  html_document: default
  fig_caption: yes
  word_document: default
---

@@

``` {r Load Data, echo=FALSE}
### data loading and cleaning up

# load cognitive effort group
setwd('./data/Cost2_data/cog')
temp = list.files(pattern="*.csv")
cogDataLong = lapply(temp, read.csv, header = FALSE)

# load wait group
setwd('../wait')
temp = list.files(pattern="*.csv")
waitDataLong = lapply(temp, read.csv, header = FALSE)

# load physical group
setwd('../phys')
temp = list.files(pattern="*.csv")
physDataLong = lapply(temp, read.csv, header = FALSE)

# load pheasysical group
setwd('../easy')
temp = list.files(pattern="*.csv")
easyDataLong = lapply(temp, read.csv, header = FALSE)

@@

nSubsW <- length(waitDataLong)
nSubsC <- length(cogDataLong)
nSubsP <- length(physDataLong)
nSubsE <- length(easyDataLong)
totalSubs <- (nSubsW + nSubsC + nSubsP + nSubsE) # why didn't I think of this before...

>>>>

---
title: "Effort and Delay Discounting in a Foraging Environment"
author: "Claudio Toro Serey & Joseph T. McGuire"
output:
  html_document: default
  pdf_document: default
  fig_caption: yes
  word_document: default
---

@@

``` {r Load Data, echo=FALSE}
### data loading and cleaning up
setwd("./data")
files <- dir(pattern = '_log.csv')
nSubjs <- length(files)

dataAll <- data_frame(SubjID = files) %>%
  mutate(contents = map(SubjID, ~ read_csv(., col_types = cols())))  %>%
  mutate(Cost = substring(SubjID, 5, 8),
         Cost = case_when(Cost == "wait" ~ "Wait",
                          Cost == "cogT" ~ "Cognitive",
                          Cost == "phys" ~ "Physical",
                          Cost == "phea" ~ "Easy"),
         SubjID = substring(SubjID, 0, 3)) %>%
  unnest() %>%
  mutate(Half = ifelse(Block < 4, "Half_1", "Half_2"))

# # load cognitive effort group
# setwd('./data/Cost2_data/cog')
# temp = list.files(pattern="*.csv")
# cogDataLong = lapply(temp, read.csv, header = FALSE)
# 
# # load wait group
# setwd('../wait')
# temp = list.files(pattern="*.csv")
# waitDataLong = lapply(temp, read.csv, header = FALSE)
# 
# # load physical group
# setwd('../phys')
# temp = list.files(pattern="*.csv")
# physDataLong = lapply(temp, read.csv, header = FALSE)
# 
# # load pheasysical group
# setwd('../easy')
# temp = list.files(pattern="*.csv")
# easyDataLong = lapply(temp, read.csv, header = FALSE)

@@

nSubsW <- length(waitDataLong)
nSubsC <- length(cogDataLong)
nSubsP <- length(physDataLong)
nSubsE <- length(easyDataLong)
totalSubs <- (nSubsW + nSubsC + nSubsP + nSubsE)
